Social Housing in Toronto

### 2024-04-21 paper/paper.qmd
commit

# Create a line plot
ggplot(plot_data, aes(x = quarter_year)) +
  geom_line(aes(y = total_active_waiting_list, color = "Total Active Applications"), size = 1.2) +
  geom_line(aes(y = Seniors, color = "Seniors' Applications"), linetype = "dashed", size = 1.2) +
  scale_color_manual(values = c("blue", "red")) +
  labs(title = "Total Active Applications vs. Seniors' Applications",
       x = "Quarter Year",
       y = "Application Numbers") +
  theme_minimal() +
  theme(legend.title = element_blank())

@@

# Assuming your dataset is loaded into a variable named 'raw_data'
# Extract relevant columns with adjusted column names
year_quarter <- raw_data$Quarter_Year
household_no_dependents <- raw_data$Household_no_dependents
household_with_dependents <- raw_data$Household_with_dependents

>>>>

# Create a plot
ggplot(plot_data, aes(x = quarter_year)) +
  geom_line(aes(y = test, color = "Total Active Applications"), size = 1.2) +
  geom_line(aes(y = Seniors, color = "Seniors' Applications"), linetype = "dashed", size = 1.2) +
  scale_color_manual(values = c("blue", "red")) +
  labs(title = "Total Active Applications vs. Seniors' Applications",
       x = "Quarter Year",
       y = "Application Numbers") +
  theme_minimal() +
  theme(legend.title = element_blank())

@@

# Extract relevant columns with adjusted column names
year_quarter <- analysis_data$Quarter_Year
household_no_dependents <- analysis_data$Household_no_dependents
household_with_dependents <- analysis_data$Household_with_dependents
